---
title: "PHAR3825 2020"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    
date: "`r format(Sys.time(), '%I:%M %p, %d %b %Y')`"
---

```{r code block 1, results='hide', message=FALSE, warning=FALSE, echo=FALSE}

source("HAR3825_Bar_Graph_2020_[function].R")
```


```{r setup, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)
library(plyr)
library(knitr)
library(kableExtra)
library(shinydashboard)
library(flexdashboard)
library(stringr)
library(plotly)
#load dataset

fileDetails <- file.info(paste0("\\Data",(list.files("\\Data", pattern= "PHAR3825_2020.*csv"))))
fileDetails <- fileDetails[with(fileDetails, order(as.POSIXct(mtime))), ]
filesListed <- rownames(fileDetails)

CSV_Location <- tail(filesListed,1)

df_orig<-read.csv(CSV_Location)

df<-df_orig  


# Groupings

df$CANVAS_SECTION_MEMBERSHIPS.47C94A6F <- gsub("3825","",df$CANVAS_SECTION_MEMBERSHIPS.47C94A6F)
df$CANVAS_SECTION_MEMBERSHIPS.47C94A6F <- str_extract(df$CANVAS_SECTION_MEMBERSHIPS.47C94A6F, "[0-9]{1,2}")
df$CANVAS_SECTION_MEMBERSHIPS.47C94A6F <- as.factor(as.numeric(df$CANVAS_SECTION_MEMBERSHIPS.47C94A6F))

df <- df[!is.na(df$CANVAS_SECTION_MEMBERSHIPS.47C94A6F),] # REmove NA Students
# levels(df$CANVAS_SECTION_MEMBERSHIPS.47C94A6F) <- c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "Groupx") 

#####
#####
library(dplyr)



#Set Standard For Graph Ordering
lookup<-read.table(header = TRUE, 
                    stringsAsFactors = FALSE, 
 text="O R r1 r2 d1 D
 1 10 8 5 Tue Tue1
 2 11 9 5 Tue Tue2
 3 8 2 2 Fri Fri3
 4 9 3 2 Fri Fri4
 5 6 10 6 Mon Mon5
 6 7 11 6 Mon Mon6
 7 4 6 4 Wed Wed7
 8 5 7 4 Wed Wed8
 9 2 4 3 Thu Thu9
 10 3 5 3 Thu Thu10
 ")

df_merge<-merge(df,lookup[,c('O','D')], by.x=c("CANVAS_SECTION_MEMBERSHIPS.47C94A6F"), by.y=c("O"))

i=6 #this number is thec column you want to read from in the code below
#Run Code for individual classes
for (z in unique(lookup[,'D'])){
  df<-df_merge
  df<-df[df$D==z,]
  df_O<-nrow(df)
  df<-ardiPHAR3825_2020_Bar_Graph(df)
  xref="x"
    if (z>0){xref=paste0("x",lookup[lookup$d1==z,i][1])}
  yref="y"
    if (z>0){yref=paste0("y",lookup[lookup$d1==z,i][1])}
  a=list(x = 12,y = 66,text = z ,xanchor='center',showarrow=FALSE, xref = xref,yref = yref, font=list(size=28, color="red"))
  df<-layout(df,title = paste0("Tutorial Group: ",z), showlegend = FALSE,xaxis=list(title = ""), yaxis=list(title = "", range = c(1,25)))#, 
    #annotations=a) 
    #list(x=3,y=10,text=z, showarrow=FALSE))
  #df<-add_trace(df,marker=list(colour="red"))
  newname<-paste0("df_",z)
  assign(newname, df)
}
#create group graph
df<-df_orig #load the original data
df_all<-ardiPHAR3825_2020_Bar_Graph(df)
df_all<-layout(df_all,title = "All Groups ", showlegend = TRUE ,xaxis=list(title = ""), yaxis=list(title = ""))



```




```{r , results='hide' , message=FALSE, warning=FALSE, echo=FALSE}
# COUNSELLING PART
source("PHAR3825_2020_Counsel_Table[function].R")


```


```{r, results='asis' , message=FALSE, warning=FALSE, echo=FALSE}

counselling_stats <- function(dat_file) {

  #Use the df_merge file where df_merge[df_merge$D==Mon5] etc

  df_bind<-ardiPHAR3825_2020_Counsel_Table(dat_file)
  rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

  i<-htmltools::tagList()

  #Results
  df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
  colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
  rownames(df_bind_results) <- c('SP','SUP','U')
  df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

  ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

  kable(df_bind_results) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Content
  df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
  colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
  rownames(df_bind_content) <- CStore

  kable(df_bind_content)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Communication
  df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
  colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
  rownames(df_bind_comms) <- CoStore
  kable(df_bind_comms)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

}



```

Quick Overview
=======================================================================
Row 
-----------------------------------------------------------------------

### Labels


```{r}
labels_checked <- sum(as.character(as.matrix(df[,grepl('Labels',colnames(df))])) %in%  c("SP","SUP","U"))
valueBox(labels_checked, 
         caption = paste0("Total number of products dispensed" ),  
         color = "#009E73")
```


Row 
-----------------------------------------------------------------------


```{r , message=FALSE, warning=FALSE, echo=FALSE}
df <- df_orig
source("PHAR3825_2020_Label_Stats.R")
Label_Stats_Out <- Label_Stats(df)
```

### Highest number of SP and SUP's
```{r}

valueBox(Label_Stats_Out$top_score,  icon = "fa-pencil")
```

### Students with highest mark
```{r}

valueBox(length(Label_Stats_Out$top_students),  icon = "fa-pencil")
```


### Highest number of U's
```{r}

valueBox(Label_Stats_Out$lowest_Score,  icon = "fa-pencil", color = "warning")
```


### Number of students with lowest mark
```{r}

valueBox(Label_Stats_Out$n_students_lowscore,  icon = "fa-pencil", color = "warning")
```


Row 
-----------------------------------------------------------------------

### Group Performance
Best :

```{r}

valueBox(Label_Stats_Out$best_group[1], 
         caption = paste0("Averaging ", round(Label_Stats_Out$best_group[2],2)," SP's per student" ),  
         icon = "fa-smile")
```

### Group Performance
SP Avg:

```{r}

valueBox(round(Label_Stats_Out$mean_group_SP[1],2), 
         caption = paste0("Average SP per student across all groups" ),  
         icon = "fa-smile")
```

### Group Performance
Worst :


```{r}
valueBox(Label_Stats_Out$worst_group[1], 
         caption = paste0("Averaging ", round(Label_Stats_Out$worst_group[2],2)," U's per student" ),  
         icon = "fa-frown", 
         color = "warning")
```

### Group Performance

U Avg:

```{r}

valueBox(round(Label_Stats_Out$mean_group_U[1],2), 
         caption = paste0("Average U per student across all groups" ),  
         icon = "fa-frown", 
         color = "warning")
```


Row 
-----------------------------------------------------------------------
```{r , message=FALSE, warning=FALSE, echo=FALSE}
source("PHAR3825_2020_Label_Stats.R")
Completion_rates <- CompletionRates(df)
```


### Schedule 1 Completion Rate

```{r}
rate <- Completion_rates[[1]][1,]
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))

```


### Schedule 2 Completion Rate

```{r}
rate <- Completion_rates[[1]][2,]
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))

```

### Schedule 3 Completion Rate

```{r}
rate <- Completion_rates[[1]][3,]
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))

```

### Schedule 4 Completion Rate

```{r}
rate <- Completion_rates[[1]][4,]
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))

```



Row 
-----------------------------------------------------------------------
```{r , message=FALSE, warning=FALSE, echo=FALSE}
source("PHAR3825_2020_Counselling_Stats.R")

```


### Counselling


```{r}
counselling_couducted <- sum(as.character(as.matrix(df[,grepl('OVERALL',colnames(df))])) %in%  c("SP","SUP","U"))
valueBox(counselling_couducted, 
         caption = paste0("Total number of counselling sessions conducted" ),  
         color = "#009E73")
```



Row 
-----------------------------------------------------------------------


### Pass Rate


```{r}
rate <- students_passing_counselling(df)
valueBox(rate$count, 
         caption = paste0("Students Passed"),  
         icon = "fa-smile")
```

### Pass Rate

```{r}
rate <- students_passing_counselling(df)
gauge(rate$rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))

```


### Pass Rate


```{r}
rate <- students_passing_counselling(df)
rate <- nrow(df) - rate$count
valueBox(rate, 
         caption = paste0("Students yet to pass"),  
         icon = "fa-frown", 
         color = "warning")
```




Row 
-----------------------------------------------------------------------

```{r,fig.height = 3, fig.width=20}

b <- student_reflection(df,1)
ggplotly(b)


```



Products {data-navmenu="2019 Comparisons" }
=======================================================================

Row {data-orientation=rows}
-----------------------------------------------------------------------

### 2019
```{r}

source("PHAR3825_Plot2019_Progress.R")

source("PHAR3825_Plot2020_Progress.R")

df_2019 <- read.csv("PHAR3825_2019_2_export") # LOAD 2019 DATA
#Plot Product Progress 2019
b <- plot_progress_2019(df_2019)$graph_2019_products
ggplotly(b)

```

### 2020

```{r}

# Plot Product Progress current
b <- plot_progress_2020(df)$graph_2020_products
ggplotly(b)

```



Counselling {data-navmenu="2019 Comparisons" }
=======================================================================

Row {data-orientation=rows}
-----------------------------------------------------------------------

### 2019
```{r}



#Plot Counselling Progress 2019
b <- plot_progress_2019(df_2019)$graph_2019_counselling
ggplotly(b)

```

### 2020

```{r}

# Plot Product Counselling current
b <- plot_progress_2020(df)$graph_2020_counselling
ggplotly(b)

```


All Groups 
=======================================================================
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Labels
```{r , message=FALSE, warning=FALSE, echo=FALSE}
df_all
```

### Counselling

```{r, results="asis" , message=FALSE, warning=FALSE, echo=FALSE}
df<-df_orig

df_bind<-ardiPHAR3825_2020_Counsel_Table(df)
rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

i<-htmltools::tagList()

#Results
df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
rownames(df_bind_results) <- c('SP','SUP','U')
df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

kable(df_bind_results) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)

# Content
df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
rownames(df_bind_content) <- CStore

kable(df_bind_content)%>%
  kable_styling(bootstrap_options = "striped", full_width = F)

# Communication
df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
rownames(df_bind_comms) <- CoStore
kable(df_bind_comms)%>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```

Monday 
=======================================================================
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Labels Group 5
```{r, message=FALSE, warning=FALSE, echo=FALSE}

df_Mon5
```

### Counselling Group 5
```{r , message=FALSE, warning=FALSE, echo=FALSE}

dat_file <- (df_merge[df_merge$D=="Mon5",])

  df_bind<-ardiPHAR3825_2020_Counsel_Table(dat_file)
  rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

  i<-htmltools::tagList()

  #Results
  df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
  colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
  rownames(df_bind_results) <- c('SP','SUP','U')
  df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

  ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

  kable(df_bind_results) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Content
  df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
  colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
  rownames(df_bind_content) <- CStore

  kable(df_bind_content)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Communication
  df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
  colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
  rownames(df_bind_comms) <- CoStore
  kable(df_bind_comms)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Labels Group 6

```{r, message=FALSE, warning=FALSE, echo=FALSE}
df_Mon6
```

### Counselling Group 6
```{r , message=FALSE, warning=FALSE, echo=FALSE}

dat_file <- (df_merge[df_merge$D=="Mon6",])

  df_bind<-ardiPHAR3825_2020_Counsel_Table(dat_file)
  rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

  i<-htmltools::tagList()

  #Results
  df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
  colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
  rownames(df_bind_results) <- c('SP','SUP','U')
  df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

  ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

  kable(df_bind_results) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Content
  df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
  colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
  rownames(df_bind_content) <- CStore

  kable(df_bind_content)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Communication
  df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
  colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
  rownames(df_bind_comms) <- CoStore
  kable(df_bind_comms)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)
```

Tuesday 
=======================================================================
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Labels Group 1
```{r , message=FALSE, warning=FALSE, echo=FALSE}
df_Tue1
```

### Counselling Group 1
```{r , message=FALSE, warning=FALSE, echo=FALSE}

dat_file <- (df_merge[df_merge$D=="Tue1",])

  df_bind<-ardiPHAR3825_2020_Counsel_Table(dat_file)
  rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

  i<-htmltools::tagList()

  #Results
  df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
  colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
  rownames(df_bind_results) <- c('SP','SUP','U')
  df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

  ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

  kable(df_bind_results) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Content
  df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
  colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
  rownames(df_bind_content) <- CStore

  kable(df_bind_content)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Communication
  df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
  colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
  rownames(df_bind_comms) <- CoStore
  kable(df_bind_comms)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Labels Group 2
```{r , message=FALSE, warning=FALSE, echo=FALSE}
df_Tue2
```

### Counselling Group 2
```{r , message=FALSE, warning=FALSE, echo=FALSE}

dat_file <- (df_merge[df_merge$D=="Tue2",])

  df_bind<-ardiPHAR3825_2020_Counsel_Table(dat_file)
  rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

  i<-htmltools::tagList()

  #Results
  df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
  colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
  rownames(df_bind_results) <- c('SP','SUP','U')
  df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

  ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

  kable(df_bind_results) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Content
  df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
  colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
  rownames(df_bind_content) <- CStore

  kable(df_bind_content)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Communication
  df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
  colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
  rownames(df_bind_comms) <- CoStore
  kable(df_bind_comms)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)
```

Wednesday 
=======================================================================
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Labels Group 7

```{r , message=FALSE, warning=FALSE, echo=FALSE}
df_Wed7
```

### Counselling Group 7
```{r , message=FALSE, warning=FALSE, echo=FALSE}

dat_file <- (df_merge[df_merge$D=="Wed7",])

  df_bind<-ardiPHAR3825_2020_Counsel_Table(dat_file)
  rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

  i<-htmltools::tagList()

  #Results
  df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
  colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
  rownames(df_bind_results) <- c('SP','SUP','U')
  df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

  ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

  kable(df_bind_results) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Content
  df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
  colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
  rownames(df_bind_content) <- CStore

  kable(df_bind_content)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Communication
  df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
  colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
  rownames(df_bind_comms) <- CoStore
  kable(df_bind_comms)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Labels Group 8

```{r , message=FALSE, warning=FALSE, echo=FALSE}
df_Wed8
```

### Counselling Group 8
```{r , message=FALSE, warning=FALSE, echo=FALSE}

dat_file <- (df_merge[df_merge$D=="Wed8",])

  df_bind<-ardiPHAR3825_2020_Counsel_Table(dat_file)
  rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

  i<-htmltools::tagList()

  #Results
  df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
  colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
  rownames(df_bind_results) <- c('SP','SUP','U')
  df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

  ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

  kable(df_bind_results) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Content
  df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
  colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
  rownames(df_bind_content) <- CStore

  kable(df_bind_content)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Communication
  df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
  colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
  rownames(df_bind_comms) <- CoStore
  kable(df_bind_comms)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)
```



Thursday 
=======================================================================
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Labels Group 9
```{r , message=FALSE, warning=FALSE, echo=FALSE}
df_Thu9
```


### Counselling Group 9
```{r , message=FALSE, warning=FALSE, echo=FALSE}

dat_file <- (df_merge[df_merge$D=="Thu9",])

  df_bind<-ardiPHAR3825_2020_Counsel_Table(dat_file)
  rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

  i<-htmltools::tagList()

  #Results
  df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
  colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
  rownames(df_bind_results) <- c('SP','SUP','U')
  df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

  ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

  kable(df_bind_results) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Content
  df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
  colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
  rownames(df_bind_content) <- CStore

  kable(df_bind_content)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Communication
  df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
  colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
  rownames(df_bind_comms) <- CoStore
  kable(df_bind_comms)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Labels Group 10
```{r , message=FALSE, warning=FALSE, echo=FALSE}
df_Thu10
```

### Counselling Group 10
```{r , message=FALSE, warning=FALSE, echo=FALSE}

dat_file <- (df_merge[df_merge$D=="Thu10",])

  df_bind<-ardiPHAR3825_2020_Counsel_Table(dat_file)
  rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

  i<-htmltools::tagList()

  #Results
  df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
  colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
  rownames(df_bind_results) <- c('SP','SUP','U')
  df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

  ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

  kable(df_bind_results) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Content
  df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
  colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
  rownames(df_bind_content) <- CStore

  kable(df_bind_content)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Communication
  df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
  colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
  rownames(df_bind_comms) <- CoStore
  kable(df_bind_comms)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)
```


Friday
=======================================================================
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Labels Group 3
```{r , message=FALSE, warning=FALSE, echo=FALSE}
df_Fri3
```

### Counselling Group 3
```{r , message=FALSE, warning=FALSE, echo=FALSE}

dat_file <- (df_merge[df_merge$D=="Fri3",])

  df_bind<-ardiPHAR3825_2020_Counsel_Table(dat_file)
  rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

  i<-htmltools::tagList()

  #Results
  df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
  colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
  rownames(df_bind_results) <- c('SP','SUP','U')
  df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

  ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

  kable(df_bind_results) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Content
  df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
  colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
  rownames(df_bind_content) <- CStore

  kable(df_bind_content)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Communication
  df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
  colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
  rownames(df_bind_comms) <- CoStore
  kable(df_bind_comms)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Labels Group 4
```{r , message=FALSE, warning=FALSE, echo=FALSE}

df_Fri4
```

### Counselling Group 4
```{r , message=FALSE, warning=FALSE, echo=FALSE}

dat_file <- (df_merge[df_merge$D=="Fri4",])

  df_bind<-ardiPHAR3825_2020_Counsel_Table(dat_file)
  rownames(df_bind)[4:(nrow(SRES_Components)+3)]<-SRES_Components[,2]

  i<-htmltools::tagList()

  #Results
  df_bind_results<-as.data.frame(df_bind[c('SP','SUP','U'),grepl('OVERALL',colnames(df_bind))])
  colnames(df_bind_results) <- colnames(df_bind)[grepl('OVERALL',colnames(df_bind))]
  rownames(df_bind_results) <- c('SP','SUP','U')
  df_bind_results[is.na(df_bind_results)]<-0 # For the graph to work. 

  ardiPHAR3825_2020_Counsel_Graph(df_bind_results)

  kable(df_bind_results) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Content
  df_bind_content<-as.data.frame(df_bind[CStore,grepl('CONTENT',colnames(df_bind))])
  colnames(df_bind_content) <- colnames(df_bind)[grepl('CONTENT',colnames(df_bind))]
  rownames(df_bind_content) <- CStore

  kable(df_bind_content)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)

  # Communication
  df_bind_comms<-as.data.frame(df_bind[CoStore,grepl('COMMUNICATION',colnames(df_bind))])
  colnames(df_bind_comms) <- colnames(df_bind)[grepl('COMMUNICATION',colnames(df_bind))]
  rownames(df_bind_comms) <- CoStore
  kable(df_bind_comms)%>%
    kable_styling(bootstrap_options = "striped", full_width = F)
```
